---
title: "Using Class *linreg*"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The RC class *linreg* allows users to complete a linear regression analysis on
a given data set, save the regression details as an object, and use the saved 
data to view plots and information about the regression.

When creating a new *linreg* object, we need two things:

1) A *formula* (an object of class "formula", e.g "Dependent ~ Independent")
2) A data.frame (*data*) that contains the parameters of the formula in the 
column names

To illustrate, let's create an example *linreg* object using the built-in data
set **iris**:

```{r, echo = FALSE}
head(iris)
cat("Total Number of Obsevations =", nrow(iris))
```

Let's say we want to look at the relationship that Sepal.Width and
Petal.Length have with Sepal.Length. To do this, we create a new *linreg* object
using the following code:

```{r}

# library(linearRegression)
# examplelinreg <- 
#   linreg$new(function = Sepal.Length ~ Sepal.Width + Petal.Length, 
#              data = iris)

```

This initializing function does three things:

1) Creates a new object **examplelinreg** with class *linreg*
2) Calculates the regression model according to the specified *function* using 
Ordinary Least Squares
3) Saves important values and information about the regression to the object

To view this information, we can call the *fields* of the object, which are 
listed below:

```{r}
# Note: n refers to the number of observations in the data set and p refers to
# the number of independent variables in the regression.

# examplelinreg$coefficients 
# Coefficient estimates for each independent variable. A matrix with one column 
# and p+1 rows.

# examplelinreg$fittedvalues 
# Fitted values of dependent variable for each observation. A matrix with one 
# column and n rows.

# examplelinreg$residuals 
# Residual values for the dependent variable for each observation. A matrix 
# with one column and n rows.

# examplelinreg$degrees 
# Degrees of Freedom of the regression. A length-one numeric vector.

# examplelinreg$residvariance 
# Residual Variance of the regression. A length-one numeric vector.

# examplelinreg$coeffvariance 
# Coefficient Variance for each independent variable. A matrix with one column 
# and p+1 rows.

# examplelinreg$tvalues 
# The T-values for each coefficient estimate. A matrix with one column and 
# p+1 rows.

# examplelinreg$pvalues 
# The P-values for each coefficient estimate. A matrix with one column and 
# p+1 rows.

# examplelinreg$sumstats 
# Summary statistics for the regression (coefficient estimates, standard errors,
# t-values, and p-values). A matrix with with four columns and p+1 rows.
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(linearRegression)
```
