---
title: "Using Class *linreg*"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Introduction

The RC class *linreg* allows users to complete a linear regression analysis on
a given data set, save the regression details as an object, and use the saved 
data to view plots and information about the regression.

When creating a new *linreg* object, we need two things:

1) A *formula* (an object of class "formula", e.g "Dependent ~ Independent")
2) A data.frame (*data*) that contains the parameters of the formula in the 
column names

To illustrate, let's create an example *linreg* object using the built-in data
set **iris**:

```{r, echo = FALSE}
head(iris)
cat("Total Number of Obsevations =", nrow(iris))
```

Let's say we want to look at the relationship that Sepal.Width and
Petal.Length have with Sepal.Length. To do this, we create a new *linreg* object
using the following code:

```{r}

library(linearRegression)
examplelinreg <- 
  linreg$new(Sepal.Length ~ Sepal.Width + Petal.Length, data = iris)

```

This initializing function does three things:

1) Creates a new object **examplelinreg** with class *linreg*
2) Calculates the regression model according to the specified *function* using 
Ordinary Least Squares
3) Saves important values and information about the regression to the object

To view this information, we can call the *fields* of the object, which are 
listed below:

```{r, eval = FALSE}
# Note: n refers to the number of observations in the data set and p refers to
# the number of independent variables in the regression.

examplelinreg$regdata
# The name of the data set being used for the regression. A character string.

examplelinreg$regformula
# The formula being used for the regression. A character string.

examplelinreg$coefficients 
# Coefficient estimates for each independent variable. A matrix with one column 
# and p+1 rows.

examplelinreg$fittedvalues 
# Fitted values of dependent variable for each observation. A matrix with one 
# column and n rows.

examplelinreg$residuals 
# Residual values for the dependent variable for each observation. A matrix 
# with one column and n rows.

examplelinreg$degrees 
# Degrees of Freedom of the regression. A length-one numeric vector.

examplelinreg$residvariance 
# Residual Variance of the regression. A length-one numeric vector.

examplelinreg$coeffvariance 
# Coefficient Variance for each independent variable. A matrix with one column 
# and p+1 rows.

examplelinreg$tvalues 
# The T-values for each coefficient estimate. A matrix with one column and 
# p+1 rows.

examplelinreg$pvalues 
# The P-values for each coefficient estimate. A matrix with one column and 
# p+1 rows.

examplelinreg$sumstats 
# Summary statistics for the regression (coefficient estimates, standard errors,
# t-values, and p-values). A matrix with with four columns and p+1 rows.
```

## Methods

As with any RC object, objects of class *linreg* have a set of functions (known
as *methods*) that apply only to them and can be called using the $ sytax as
shown above. In particular, there are six main methods that can be called: 
print(), pred(), resid(), coef(), summary(), and plot(). Here, we will explain 
what each method does and how to use them:

### print()

The print() method prints the coefficient estimates for the independent
variables. It also displays the formula, the name of the data set, and the 
names of the variables.

```{r}
examplelinreg$print()
```

### pred()

The pred() method displays the predicted/fitted values of the dependent
variable for every observation in the data set according to the model.

```{r}
head(examplelinreg$pred())
```

### resid()

The resid() method is similar to pred(), but instead of displaying the fitted
values, it shows the difference between the real values and the predicted
values, or the *residuals*.

```{r}
head(examplelinreg$resid())
```

### coef()

Similar to print(), the coef() method displays the coefficient estimates for
the regression model. However, coef() returns the values as a named vector and
does not include information about the formula and data.

```{r}
examplelinreg$coef()
```

### summary()

The summary() method displays the summary statistics for the regression model.
In particular, it shows us the coefficient estimate, standard error, t-value,
p-value, and significance level for each independent variable, as well as the
residual standard error and degrees of freedom.

```{r}
examplelinreg$summary()
```

### plot()

The plot() method
